Synthesizing Quotient Lenses

### 2017-10-18 papers/QuotientLensSynth/main.tex
update performance, todo add graph

We summarize the results of these experiments in Figure~\ref{?}.  \Name{} was
able to synthesize all of Optician's benchmarks at a speed competitive with
Optician.  Furthermore, adopting these tasks to use QREs actually sped up
tasks!  After canonization, the regular expressions sent to synthesis are
\emph{smaller} than before canonization - making the bijective lens synthesis
portion of these tasks easier.

>>>>

We summarize the results of these experiments in Figure~\ref{?}.  \Name{} was
able to synthesize all of Optician's benchmarks at a speed competitive with
Optician.  There was additional overhead in calculating $W(q)$ and $K(q)$,
resulting in a very slight decrease in performance.

Also notable was one of the data.gov examples, which converted demographic
statistics by zip code from xml form into rdf form.  This merely took longer because it was
an exceptionally large format, converting over 40 fields.  After adding in additional
fields to make this format bijective, it still took over 15 seconds to complete.
